Statistics Project

### 2022-12-10 rough_analysis.Rmd
Updated selection models, may have accounted for colinearity in aggressive/unintended manner. Doublecheck!

```{r include=FALSE}
library(tidyverse)
library(plotly)
library(car)
library(caret)
library(olsrr)
```

@@

For Analysis 2, we need to generate 4 models using variations of parameters selected by Forwards Parameter Selection, Backwards Elimination, Stepwise Selection, and a 
personalized custom approach.

@@

#forwards selection: 
forward = ols_step_forward_p(fit_numeric, penter = 0.05, details = FALSE)

backwards = ols_step_backward_p(fit_numeric, prem = 0.05, details = FALSE)

stepwise = ols_step_both_p(fit_numeric, pent = 0.05, prem =0.05, details = FALSE)
```

@@

This step might not be necessary but could improve the quality of the model. Analysis shows a marginal improvement to R^2 and marginal deteriorate to PRESS Stat when rm'ing outliers.

@@

ModelRMSE(transForward$model$residuals) #see defined functions at top of document
CVPress(transForward$model)

@@

>>>>

```{r include=FALSE}
library(tidyverse)
library(plotly)
library(car)
library(caret)
library(olsrr)
library(corrplot)
```

Defining functions for future use, I didn't know where to put this:

@@

For Analysis 2, we need to generate 4 models using variations of parameters selected by Forwards Parameter Selection, Backwards Elimination, StepWise Selection, and a 
personalized custom approach.

@@

#forwards selection: 
forward = ols_step_forward_p(fit_numeric, penter = 0.05, details = FALSE)
#backwards
backwards = ols_step_backward_p(fit_numeric, prem = 0.05, details = FALSE)
#stepwise
stepwise = ols_step_both_p(fit_numeric, pent = 0.05, prem =0.05, details = FALSE)
```

@@

This step might not be necessary but could improve the quality of the model. Analysis shows a marginal improvement to R^2 and marginal deterioration to PRESS Stat when rm'ing outliers.

@@

summary(transForward$model)
ModelRMSE(transForward$model$residuals) #see defined functions at top of document
CVPress(transForward$model)

@@

```{r Reduced Linearity Set}
t1 = subset(transformed_numeric, select = -c(LotFrontage, MasVnrArea, GarageYrBlt, OverallQual, TotRmsAbvGrd, GarageCars, TotalBsmtSF, X1stFlrSF, X2ndFlrSF, FullBath )) #removal of largely correlated values to reduce multicollinearity (VIF /approx 1) and actually allow back-elimination to run, it wasn't running without a ton of errors without this.

corrplot(cor(t1)) #visualize correlation to identify which plots are correlated. After elimiation, it should be fairly sparsely correlated.

t1fit = lm(SalePrice ~. , data = t1)

backt1 = ols_step_backward_p(t1fit, prem = 0.05, details = FALSE)
forwardt1 = ols_step_forward_p(t1fit, penter = 0.05, details = FALSE)                #the p-values for these should be fiddled with to test a better selection set, although could be unnec. 
stepwiset1 = ols_step_both_p(t1fit, pent = 0.05, prem =0.05, details = FALSE)

#---------------------------------Summary Stats of the produced RL sets
summary(backt1$model)
vif(backt1$model)

ModelRMSE(backt1$model$residuals)
CVPress(backt1$model)
#---------------------------------
summary(forwardt1$model)
vif(forwardt1$model)

ModelRMSE(forwardt1$model$residuals)
CVPress(forwardt1$model)
#---------------------------------
summary(stepwiset1$model)
vif(stepwiset1$model)

ModelRMSE(stepwiset1$model$residuals)
CVPress(stepwiset1$model)

```

Now that we have generated 3 models (Need 4!!!) we can predict the saleprice on a test set of data, submit this modelled set to Kaggle to generate a Kaggle Score for the model. That is done as following;

```
